Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
adding subsections in 5 to match 4 - adding a link in 4 to a subsection in 5 (software papers)

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software. While some journals (e.g., F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals
\cite{aas-sofware-papers}. As the publishers of journals and conveners of domain-specific conferences the authors note the potential importance of professional societies in effecting changes in community practice. \katznote{I can't quite understand what the prev sentence says}

@@

\textbf{What software to cite}

@@

\textbf{Software papers}

@@

\textbf{Derived software}

@@

\textbf{Software peer review}

@@

\textbf{Citations in text}

@@

\textbf{Unique identification}

@@

\textbf{Access to software}

@@

\textbf{Updates to this document}

>>>>

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software, often known as software papers (see \S\ref{sec:software_papers}).
While some journals (e.g., F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals
\cite{aas-sofware-papers}. As the publishers of journals and conveners of domain-specific conferences the authors note the potential importance of professional societies in effecting changes in community practice. \katznote{I can't quite understand what the prev sentence says}

@@

\subsection{What software to cite}

@@

\subsection{Software papers} \label{sec:software_papers}

@@

\subsection{Derived software}

@@

\subsection{Software peer review}

@@

\subsection{Citations in text}

@@

\subsection{Unique identification}

@@

\subsection{Access to software}

@@

\subsection{Updates to this document}
